Simplifying Lotka--Volterra interaction matrices by species grouping: optimal groupings are unpredictable

### 2022-08-03 supp.rnw
Change "fitted" to "predicted" in the supplementary model fit plot axis labels.
To demonstrate that this is the predicted output from the whole model,
not just the fitted growth rate parameter.

		plot <- ggplot2::ggplot(plot_df, ggplot2::aes(x = observed, y = fitted)) +
			ggplot2::geom_point() +
			ggplot2::geom_smooth(method = lm, formula = y~x) +
			ggplot2::geom_abline(slope = 1, intercept = 0) +
			ggplot2::facet_wrap(.~focal) +
			ggplot2::labs(x = "Observed growth rate (per capita)", y = "Fitted growth rate (per capita)")
		return(plot)
	}

>>>>

		plot <- ggplot2::ggplot(plot_df, ggplot2::aes(x = observed, y = fitted)) +
			ggplot2::geom_point() +
			ggplot2::geom_smooth(method = lm, formula = y~x) +
			ggplot2::geom_abline(slope = 1, intercept = 0) +
			ggplot2::facet_wrap(.~focal) +
			ggplot2::labs(x = "Observed growth rate (per capita)", y = "Predicted growth rate (per capita)")
		return(plot)
	}
